DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
improved illustrative example
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
namely poles must have the modulus less than one. In order to compute the poles for the digital 
system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
to achieve a general equation regarding the transfer function representation.

The general equation that represents the combination between Equations~\eqref{equation_plant}
and~\eqref{equation_controller} using the \texttt{series} configuration (as shown in Figure~\ref{fig:typical-control-system}) is
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{1.069z^{4} - 1.136z^{3} + 0.4849z^{2} -0.8704z + 0.5317}.
\end{equation}

For the stability check, if any root has modulus equal or greater than one, then the system is unstable; 
otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
in MATLAB~\cite{matlab-toolbox} result in the following poles: 
$-0.2909 + 0.8065i$, $-0.2909 - 0.8065i$, $0.8553$ and $0.7924$, 
which means that DSSynth has synthesized a stable digital controller.

>>>>

A digital system is stable \textit{iff} all of its poles are inside the $z$-plane unity circle, 
namely poles must have the modulus less than one. In order to compute the poles for the digital 
system represented by Equations~\eqref{equation_plant} and \eqref{equation_controller}, 
the user can invoke the \texttt{feedback} and \texttt{series} commands in MATLAB~\cite{matlab-toolbox} 
to achieve a general equation regarding the transfer function representation as shown in Figure~\ref{combine-controller-plant}.

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.99832 0.09587 0.1926];
>> den = [1 0.5665 0.75];
>> controller = tf(num,den,0.002);
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> plant = tf(num,den,0.002);
>> sys = series(controller,plant)
>> sys =
>> 
>>      0.06863 z^4 - 0.006591 z^3 - 0.01324 z^2
>>  ------------------------------------------------
>>  z^4 - 1.129 z^3 + 0.4981 z^2 - 0.8704 z + 0.5317
\end{lstlisting}
\vspace{-0.2cm}
\caption{General equation for the closed-loop control system using the series configuration (as shown in Figure~\ref{fig:typical-control-system}).}
\label{combine-controller-plant}
\end{figure}

The general equation that represents the closed-loop control system using the series 
configuration is described by Equation~\ref{equation_general} as follows
%
\begin{equation}
\small
\label{equation_general}
\frac{N(z)}{D(z)}=\frac{0.06863z^{4} - 0.006591z^{3} - 0.01324z^{2}}{z^{4} - 1.129z^{3} + 0.4981z^{2} -0.8704z + 0.5317}.
\end{equation}

For the stability check, if any root of the polynomial $D(z)$ in Equation~\ref{equation_general} 
has modulus equal or greater than one, then the system is unstable; 
otherwise, it is stable. Indeed, the roots computed by the function \texttt{roots} 
in MATLAB~\cite{matlab-toolbox} result in the following poles as shown in Figure~\ref{roots-of-dz}, 
which means that DSSynth has synthesized a stable digital controller.

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> den = [1 -1.129 0.4981 -0.8704 0.5317]
>> r = roots(den)
>> r =
>>  -0.2833 + 0.8185i
>>  -0.2833 - 0.8185i
>>   0.9480 + 0.0000i
>>   0.7476 + 0.0000i
\end{lstlisting}
\vspace{-0.2cm}
\caption{Roots of the polynomial $D(z)$ given by Equation~\ref{equation_general}.}
\label{roots-of-dz}
\end{figure}
